Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-22 manuscript/bodycssa19.tex
Call out TJ and Olufemi in Acks.

\begin{acks}
We thank Milton Friesen and Srikanth Mudigonda, the authors of ~\cite{srimil} for providing the code for resource pooling. This work is part of a larger project undertaken by ABMSPECSIG\footnote{https://github.com/WheezePuppet/specstar} team. We thank everyone in the team for help in various stages of this work. The authors wish to thank their respective home institutions where this work was done.  
\end{acks}

>>>>

\begin{acks}
We thank Milton Friesen and Srikanth Mudigonda, the authors of ~\cite{srimil}, for providing the code for resource pooling; Thomas Davies for contributions to the code base; and Olufemi Olaba for modeling ideas. This work is part of a larger project undertaken by ABMSPECSIG\footnote{https://github.com/WheezePuppet/specstar} team. The authors wish to thank their respective home institutions where this work was done.
\end{acks}
